Exploring and Reverse Engineering the Motives Behind API Modifications

### 2015-03-27 rmtw/a6/latex8.tex
Updated incorrect reference
dsfsa

%%Integrate this with Introduction:
%Furthermore, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{mcdonnell2013empirical}. The study aimed to discover if APIs with high rates of faults affected the success of an application. The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{mcdonnell2013empirical}.

@@

A combination of the analysis between the changes to APIs, Lehmans laws and the software evolution categories \cite{chapin2001types} (!!!cites) allowed us to answer RQ1. The ability to answer RQ1 was the basis upon which we determined the answer to RQ2.

>>>>

%%Integrate this with Introduction:
%Furthermore, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{linares2013api}. The study aimed to discover if APIs with high rates of faults affected the success of an application. The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{linares2013api}.

@@

A combination of the analysis between the changes to APIs, Lehman's laws and the software evolution categories \cite{chapin2001types} (!!!cites) allowed us to answer RQ1. The ability to answer RQ1 was the basis upon which we determined the answer to RQ2.
